Predicting Bike Usage at UofT St. George with Bayesian Poisson Regression

### 2024-12-01 paper/paper.qmd
minor mistake in graph fixed
minor mistake in graph fixed

ggplot(data = total_counts, aes(x = time_interval, y = count, fill = time_interval)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(percentage, 1), "%")),
            vjust = -0.5, size = 3) +
  labs(x = "Time interval", y = "Total usage") +
  scale_y_continuous(labels = scales::comma) + 
  theme_minimal() +
  theme(legend.position = "none")

>>>>

ggplot(data = total_counts, aes(x = time_interval, y = count, fill = time_interval)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(percentage, 1), "%")),
            vjust = -0.5, size = 3) +
  labs(x = "Time interval", y = "Total usage") +
  scale_y_continuous(labels = scales::comma) + 
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 10, hjust = 1)
  )
